Vision-Based Automatic Landing of Drones

### 2024-10-21 Article/Article.tex
Add Conclusion section

\section{Conclusion}

>>>>

\section{Conclusion}
In this work, we presented a novel approach for autonomous drone landing using a visual-based framework that eliminates the need for GPS. Our algorithm, tested on a DJI drone equipped with a standard camera, successfully integrates object detection, edge detection, and flight control to enable precise landings. The system's performance in controlled environments demonstrates its effectiveness, especially in scenarios where GPS signals are unreliable or unavailable.\\

However, there are still challenges to address, particularly in handling unpredictable wind conditions and ensuring the system’s reliability in diverse outdoor environments. Future work will focus on improving the algorithm’s robustness in real-world scenarios and enhancing its functionality through additional features such as offline speech recognition and plane recognition algorithms for safer and more autonomous landings.\\

The combination of these developments will pave the way for safer, more reliable, and efficient drone operations in a wide variety of applications, from urban package delivery to military surveillance missions.
